A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-01-27 paper.tex
5d in intro, and minor fixes

\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theories}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

@@

\textbf{Dimension 5}
\begin{itemize}
 \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.} \cite{KallenZabzine}
 \item \emph{$\mc N=2$ intermediate twist.} \cite{ElliottPestun}
 \item \emph{$\mc N=2$ topological A twist.} \cite{Anderson, QiuZabzine}
 \item \emph{$\mc N=2$ topological B twist.} \cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}
\end{itemize}

@@

\subsubsection{Rank $(1, 2)$ twist}

@@

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{4d12hodge} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$. Moreover, this equivalence is $\U(2)$-equivariant.
\label{thm:4d12hodge}
\end{theorem}

\subsubsection{Rank (2, 2) twist}
\label{sect:4dqgltwist}

>>>>

\title{A Taxonomy of Twists of Supersymmetric Yang--Mills Theory}
\author{Chris Elliott\and Pavel Safronov \and Brian Williams}

@@

\textbf{Dimension 5}
\begin{itemize}
 \item \emph{$\mc N=1$ and $\mc N=2$ minimal twist.}  There is a minimal twist in 5 dimensions which can be defined with $\mc N=1$ supersymmetry in the presence of a $U$-valued hypermultiplet, obtained by dimensional reduction from 6d $\mc N=(1,0)$.  This twist is equivalent to a mixed form of Chern-Simons theory with one topological direction and two complex holomorphic directions, coupled to a partially holomorphic symplectic boson.  It is invariant for the metalinear group $\MU(2)$ for general $U$, and for $\mr U(2)$ when $U = T^*R$ is of cotangent type, and can be defined on the product of a flat 1-manifold and an arbitrary complex surface (with a choice of square root of the canonical bundle in the general case).  This theory was studied by K\"all\'en and Zabzine  \cite{KallenZabzine}.  If $U = T^*\gg$ the supersymmetry action can be promoted to the $\mc N=2$ supersymmetry algebra, and the twisted theory can be identified with a mixed form of BF theory valued in the adjoint quotient $\gg/\gg$.
 \item \emph{$\mc N=2$ intermediate twist.} In the $\mc N=2$ case there is an intermediate twist, with four invariant directions.  This twist can be identified with a generalized BF theory with three topological directions and one complex holomorphic direction.  It is invariant for the group $\spin(2;\RR) \times \spin(3;\RR)$ and can be defined on the product of a 2-manifold and a 3-manifold, each equipped with a spin structure.  This twist was considered in \cite{ElliottPestun} on manifolds of the form $\Sigma \times C \times S^1$, where $\Sigma$ and $C$ are Riemann surfaces, where the moduli space can be viewed as a multiplicative version of the Hitchin system.
 \item \emph{$\mc N=2$ topological A twist.} There are two topological twists in 5d $\mc N=2$.  One, which we refer to as the A-twist, arises by dimensionally reducing the topological twist of 6d $\mc N=(1,1)$ super Yang-Mills theory.  It is perturbatively trivial, but can be realized non-trivially as the generic point in a 1-parameter degeneration of the intermediate twist.  The full family is invariant for the group $\Spin(3;\RR)$.  This theory was studied by Qiu and Zabzine, \cite{QiuZabzine}, where the equations of motion were shown to include the Haydys-Witten equations.  Twisting homomorphisms in this situation were previously studied by Anderson \cite{Anderson}.
 \item \emph{$\mc N=2$ topological B twist.} Finally, the other topological twist, associated to a rank 4 supercharge, can be identified with 5d Chern-Simons theory.  This theory is only $\ZZ/2\ZZ$-graded, and it is invariant for the group $\spin(3;\RR)$.  This twist was identified in work of Geyer-M\"ulsch and of Bak-Gustavsson\cite{GeyerMuelsch, BakGustavsson1,BakGustavsson2}.
\end{itemize}

@@

\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} twist}

@@

\begin{theorem}
The twist of 4d $\cN=4$ super Yang--Mills with respect to the family $Q_t$ of square-zero supercharges of Equation \ref{eq:4d412Hodgefamily} is perturbatively equivalent to $\map\left(\CC^2_{\rm Dol}, B\fg_{\Hod}\right)$. Moreover, this equivalence is $\U(2)$-equivariant.
\label{thm:4d12hodge}
\end{theorem}

\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
\label{sect:4dqgltwist}
